Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
revised the introduction

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.  However, to better understand successful 
project contributions, we must take into consideration and analyze 
different social attributes from the developers creating the commits,
which can be great predictors for the success of a contribution.

Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
These kinds of mechanisms benefit in substancial part by knowing into which 
aspects to look for as predictors of the quality of the contribution being made.

In this study we analyze a large set of technical and social attributes 
and how these can be used to
add certainty to the probability of a contribution being successful or not. 
Our corpus is based on the entries of a large number of open source projects
using continuous integration. Continuous integration automatically checks
the contribution against the project's test cases, to notify the development
team if the change caused a test case failure~\cite{Meyer14}. The
projects using continuous integration provide quality standard barriers such as
test cases which will cause the build to break if the commit does not perform
accordingly to the standards. When a change
passes these vetting techniques, it shows that the project developers
have confidence in the changes, therefore, allowing us to analyze the success
of the contributions made by passing the quality standards created by the 
core developers of each project.

In past studies, both technical factors and social factors have been found to be
important when predicting pull request success~\cite{tsay14icse,tsay14fse}.
In this study we are interested in analyzing the quality of a contribution 
at a lower granulairity level, commit level. We will analyze this in the 
context of continuous integration, using some of the social attributes provided
by GitHub as a proxy for the developer's experience level and familiarity with
the process, and their importance when grouped with technical attributes of the commit as 
confounds for the complexity of the commit being pushed.

The knowledge obtained by 
analyzing how much impact social characteristics have on the success of a commit 
integration will help developers further understand what social attributes are 
better proxies for experience and coding excellence; and it will also help code 
integrators and core team members to know how to prioritize pull requests coming 
from different developers, which of them may have a higher probability of 
integration success based not only on the technical difficulty of the 
integration, but also on social factors that determine the expertise of the 
developer in their integration practices.

>>>>

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.  Yet, as social coding sites continue to get
more users and specific projects become more popular, projects receive more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions.

Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. Another
contribution mechanism these projects use is continuous
integration, which notifies the team members if a change caused a test 
failure~\cite{Meyer14}.
Yet, these methods can become a bottleneck.
To avoid a possible bottleneck, it would be beneficial to prioritize certain
contributions.  This prioritize can be achieved with predictors of the
contribution's quality.

Past projects have shown that both technical factors, which describe the commit
and the project receiving the commit, and social factors, which describe the
developer making the commit, have been found useful when predicting a
contribution's quality~\cite{tsay14icse,tsay14fse}.
In this study we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis with a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects pass integration tests, 
it shows that the project developers
have confidence in the changes. 
Thus, we can use the build integration status of the commit as documentation of
the commit's quality.

While past studies have analyzed pull request
success~\cite{tsay14icse,tsay14fse}, we are interested in analyzing the quality 
of a contribution 
at a lower granulairity level: individual commits. \todo{Zack question for Mau:
did we really do the investigation at the individual commit level?} 
We analyzed commits in the 
context of continuous integration, using the technical factors found in the 
some of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.

This study investigates how well different technical and social factors predict
commit quality.  This information will help core team members prioritize project
contributions.  It will also provide a further understand of quality enforcement
in the software development process.
